Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-14 paper.tex
FIX typos

\documentclass[11pt, a4paper]{article}
\usepackage[onehalfspacing]{setspace}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.25in]{geometry}
\usepackage[round]{natbib}

@@

\section{The regression setup and its problem}
\label{regression}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$,  \citet{campbell2006efficient} consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}.
\end{align}
They further assume normality, i.e., 
\begin{equation}
w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma})
\end{equation} where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known.

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A common approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being unacceptably larger than nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, \citet{campbell2006efficient} start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus, the t-test ignores information about $\rho$.

To reason about how to incorporate information about $\rho$ into the test \citet{campbell2006efficient} assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right) = & 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, \citet{campbell2006efficient} propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%. For very large sample sizes of more than 1000 observations, a single spike of over-rejection is found when the GARCH process is very near nonstationary. Otherwise, rejection rates are close to the nominal size.

@@

\setlength\tabcolsep{5.3pt}

@@

Based on an extended dataset taken from Amid Goyal's website, only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First, returns in the extended dataset are of the S\&P500 instead of the CRSP value-weighted index. Also, due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since \citet{campbell2006efficient} use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos}, predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  

@@

Since the original publication of \citet{campbell2006efficient} a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 5\% significance level for any of the regressors and sampling frequencies considered. Both regressors are still highly persistent at all sampling frequencies, demonstrated by the confidence interval for $\rho$ containing unity in all cases. 
\begin{table}[h!]
\small
\setlength\tabcolsep{5.3pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. The code generating this table is available at https://github.com/jpwoeltjen/PersistentRegressors. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\documentclass[12pt, a4paper]{article}
\usepackage[onehalfspacing]{setspace}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.1in]{geometry}
\usepackage[round]{natbib}

@@

\section{The regression setup and its problem}
\label{regression}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$,  \citet{campbell2006efficient} consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}.
\end{align}
They further assume normality, i.e., 
\begin{equation}
w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma}),
\end{equation} where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known.

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A naïve approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being unacceptably larger than nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, \citet{campbell2006efficient} start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and thus cannot be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus, the t-test ignores information about $\rho$.

To reason about how to incorporate information about $\rho$ into the test, \citet{campbell2006efficient} assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right) = & 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, \citet{campbell2006efficient} propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%. For very large sample sizes of more than 1000 observations, a single spike of over-rejection is found when the GARCH process is very near nonstationarity. Otherwise, rejection rates are close to the nominal size.

@@

\setlength\tabcolsep{5.0pt}

@@

Based on an extended dataset taken from Amid Goyal's website, Table~\vref{tab:extended} shows that only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First, returns in the extended dataset are of the S\&P500 instead of the CRSP value-weighted index. Also, due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since \citet{campbell2006efficient} use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos}, predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  

@@

Since the original publication of \citet{campbell2006efficient} a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 5\% significance level for any of the regressors and sampling frequencies considered. Both regressors are still highly persistent at all sampling frequencies, demonstrated by the confidence interval for $\rho$ containing unity in all cases. 
\begin{table}[h!]
\small
\setlength\tabcolsep{5.0pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. The code generating this table is available at https://github.com/jpwoeltjen/PersistentRegressors. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}
